Simulation study

### 2021-11-21 SPsims/SPsim.Rmd
Split off running SAS from loading results

```{r RunSAS}
if (.Platform$OS.type == "unix"){
  system("sas FitModels", wait=TRUE)
}
gee.res <- read.delim("GEEest.txt") %>%
  mutate(Coef = paste0(Parm, Level1)) %>%
  select(-Parm,-Level1) %>%
  group_by(Dataset) %>%
  spread(key=Coef, value=Estimate)

>>>>

```{r RunSAS}
if (.Platform$OS.type == "unix"){
  system("sas FitModels", wait=TRUE)
}
```

```{r LoadResults}
gee.res <- read.delim("GEEest.txt") %>%
  mutate(Coef = paste0(Parm, Level1)) %>%
  select(-Parm,-Level1) %>%
  group_by(Dataset) %>%
  spread(key=Coef, value=Estimate)
